%!TEX ROOT=Thesis.tex

\chapter{SOTA}

Smart way of Google street view images\cite{Developers.google.com2018} as data set and using Machine learning algorithm specifically deep learning  to develop a software solution has been seen in last few years. some such application are \cite{Kita-wojciechowska} where images of house from GSV is annotated manually and and this data is use to predicts car accident of its resident. Other such application is taking use of GSV and satellite images to extract features like age,size and accessibility using Deep Neural Network to estimate the house prices.  

With the buzz of autonomous driving Layered Interpretation of Street View Images \cite{bibid} was developed in Mitsubishi Electric Research Labs with deep neural network on GSV images.In paper ,they proposed a layered street view model to encode both depth and semantic information on street view images for autonomous driving. They propose a 4-layer street view model, layers encode semantic classes like ground, pedestrians, vehicles, buildings, and sky in addition to the depths. The only input to our algorithm is a pair of stereo images. Deep neural network was used to extract the appearance features for semantic classes.

Another example of application developed with GSV and deep neural network is Building instance classification using street view images\cite{Kang2018} ,Land-use classification based on spaceborne or aerial remote sensing images has been extensively studied over the past decades. Proposed a general framework for classifying the functionality of individual buildings. The proposed method is based on Convolutional Neural Networks (CNNs) which classify facade structures from street view images, such as Google StreetView\cite{}, in addition to remote sensing images which usually only show roof structures. Geographic information was utilized to mask out individual buildings, and to associate the corresponding street view images. In addition, the method was applied to generate building classification maps on both region and city scales of several cities in Canada and the US

One of the such exampple which is similar to work done in the project is Automatic Discovery and Geotagging of Objects from Street View Imagery \cite{bibid} This paper describe about solution to localize the object from multiple view using geometry.To geolocate the object in image they developed Markov Field model to perform object triangulation.They use 2 SOTA  FCNN for semantic segmentation and monocular depth estimation.The geolocalization is done with Google street view images with Triangular based MRF model descriped in paper. End Result of the projects looks similar to the output of the resulting output but lacks the precision which is done with the help of depth image and Triangulation-based MRF model.The end result is a vectorized map with overlay of tags in map.

