\documentclass{ctuthesis}

\usepackage{graphicx}

\ctusetup{
	xdoctype = M,
	xfaculty = F3,
	mainlanguage = english,
	titlelanguage = english,
	title-english = {Deep neural network for city mapping using Google Street View data},
	%	title-czech = {Sázení uranu},
	department-english = {Department of Cybernetics},
	author = {Varun Burde},
	supervisor = {Ing.Michal Reinštein,Ph.D.},
	supervisor-address = {E225b,\\ Karlovo nam. 13,\\ 121 35 Prague 2,\\ Czech Republic},
	month = 5,
	year = 2019,
}

\ctuprocess


\begin{abstract-english}
With the advancement computation power and large datasets finally made a huge improvement of Deep neural network leading many widespread applications. One of such application is solving computer vision problems like classification and segmentation. Also Competition like ImageNet\cite{StanfordVisionLab2015} Large Scale Visual Recognition Challenge, took the solution to next level, in some cases classification is better than Human. 
 
This report describes the evaluation of pre-trained deep neural network on Google StreetView Images\cite{Developers.google.com2018}. Pretrained model of Mask RCNN\cite{He2017} for matterport \cite{}.Implementation is done in Python\cite{PythonSoftwareFoundation2019} using Keras  and TesnsorFlow-GPU framework. User interface for the application execution, processing of the input images and visualization of the results is realized using Google Colab\cite{Colab.research.google.com} with repository in GIT\cite{Conservancy}.

A pipeline was created for the task, user provide the parameters like coordinates for the Google StreetView API \cite{Developers.google.com2018}. Python\cite{PythonSoftwareFoundation2019} script downloads the available images to that location then images were pre-processed to fit into classifier. Classification is done on the Images depending on the architecture of the Neural Network.A vectorized map is generated as a result of classified Images and put into map using Folium. 

Map is represented in various form as heat-map for better understanding of scenario. Object markers in map are the objects classified with the Mask RCNN .
	
\end{abstract-english}

\begin{abstract-czech}
	Rozvíjíme \ldots
	
\end{abstract-czech}

\begin{document}
		
\maketitle	

\input{introduction}

\input{SOTA}

\input{theory}

\input{Method}

\input{Implementaion}

\input{exper}

\input{conclusion}
		
\chapter{Bibliography}

\bibliographystyle{ieeetr}	
\bibliography{thesis}

\end{document}

